The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add bit about chemo-dynamical tagging
Add values of A, B, C for Sag

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for the toy simulation of a Sagittarius encounter
\citep{2018MNRAS.481..286L}. Again we have subtracted a best fit curve of the
form $\text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}$, with the values
for $\text{A}$, $\text{B}$, and $\text{C}$ being \Gus{something},
\Gus{something}, and \Gus{something else}, respectively. In the first two
panels, we see that the midplane is relatively flat in the inner galaxy. But
additional encounters drive strong midplane variation. In the third panel, we
see a strong $m=2$ mode develop, consistent with the $R=8\,\kpc$ panel of
Figure~17 in \citet{2018MNRAS.481..286L}.

@@

>>>>

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for the toy simulation of a Sagittarius encounter
\citep{2018MNRAS.481..286L}. Again we have subtracted a best fit curve of the
form $\text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}$, with the values
for $\text{A}$ being $9.5, 2.5, -212, -394\,\pc$, for $\text{B}$ being
$0.0013, 0.0007, -0.63, -1.00\,\text{rad}$ and $\text{C}$ being $2.6, -7.8,
-65, -53\,\pc$. Each of these values are for each successive timestep. In the
first two panels, we see that the midplane is relatively flat in the inner
galaxy. But additional encounters drive strong midplane variation. In the
third panel, we see a strong $m=2$ mode develop, consistent with the
$R=8\,\kpc$ panel of Figure~17 in \citet{2018MNRAS.481..286L}.

@@

\item This work emphasizes the importance of combining chemistry and dynamics.
Chemical tagging \citep{2002ARA&A..40..487F} and dynamical tagging must
complement and confirm each other. This was also recently pointed out by
\Gus{someone}.
